---
title: "VE320 Homework3"
author: "Liu Yihao 515370910207"
date: "2018-06-13"
output: 
  pdf_document:
    includes:
      in_header: header.tex
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(latex2exp)
```

## Ex 3.1

### (a)
$$n_i=2.4\times10^{13}\unit{cm^{-3}}$$

#### (i)
$$\frac{N_d-N_a}{2}=\frac{2\times10^{15}\unit{cm^{-3}}}{2}=10^{15}\unit{cm^{-3}}$$
$$
\begin{aligned}
n_0&=\frac{N_d-N_a}{2}+\sqrt{\left(\frac{N_d-N_a}{2}\right)^2+n_i^2}\\
&=10^{15}\unit{cm^{-3}}+\sqrt{(10^{15}\unit{cm^{-3}})^2+(2.4\times10^{13}\unit{cm^{-3}})^2}\\
&=2.000\times10^{15}\unit{cm^{-3}}
\end{aligned}
$$
$$p_0=\frac{n_i^2}{n_0}=\frac{(2.4\times10^{13}\unit{cm^{-3}})^2}{2.000\times10^{15}\unit{cm^{-3}}}=2.88\times10^{11}\unit{cm^{-3}}$$

#### (ii)
$$\frac{N_a-N_d}{2}=\frac{10^{16}\unit{cm^{-3}}-7\times10^{15}\unit{cm^{-3}}}{2}=1.5\times10^{15}\unit{cm^{-3}}$$
$$
\begin{aligned}
p_0&=\frac{N_a-N_d}{2}+\sqrt{\left(\frac{N_a-N_d}{2}\right)^2+n_i^2}\\
&=1.5\times10^{15}\unit{cm^{-3}}+\sqrt{(1.5\times10^{15}\unit{cm^{-3}})^2+(2.4\times10^{13}\unit{cm^{-3}})^2}\\
&=3.000\times10^{15}\unit{cm^{-3}}
\end{aligned}
$$
$$n_0=\frac{n_i^2}{p_0}=\frac{(2.4\times10^{13}\unit{cm^{-3}})^2}{3.000\times10^{15}\unit{cm^{-3}}}=1.92\times10^{11}\unit{cm^{-3}}$$

### (b)
$$n_i=1.8\times10^{6}\unit{cm^{-3}}$$

#### (i)
$$\frac{N_d-N_a}{2}=\frac{2\times10^{15}\unit{cm^{-3}}}{2}=10^{15}\unit{cm^{-3}}$$
$$
\begin{aligned}
n_0&=\frac{N_d-N_a}{2}+\sqrt{\left(\frac{N_d-N_a}{2}\right)^2+n_i^2}\\
&=10^{15}\unit{cm^{-3}}+\sqrt{(10^{15}\unit{cm^{-3}})^2+(1.8\times10^{6}\unit{cm^{-3}})^2}\\
&=2.000\times10^{15}\unit{cm^{-3}}
\end{aligned}
$$
$$p_0=\frac{n_i^2}{n_0}=\frac{(1.8\times10^{6}\unit{cm^{-3}})^2}{2.000\times10^{15}\unit{cm^{-3}}}=1.62\times10^{-3}\unit{cm^{-3}}$$

#### (ii)
$$\frac{N_a-N_d}{2}=\frac{10^{16}\unit{cm^{-3}}-7\times10^{15}\unit{cm^{-3}}}{2}=1.5\times10^{15}\unit{cm^{-3}}$$
$$
\begin{aligned}
p_0&=\frac{N_a-N_d}{2}+\sqrt{\left(\frac{N_a-N_d}{2}\right)^2+n_i^2}\\
&=1.5\times10^{15}\unit{cm^{-3}}+\sqrt{(1.5\times10^{15}\unit{cm^{-3}})^2+(1.8\times10^{6}\unit{cm^{-3}})^2}\\
&=3.000\times10^{15}\unit{cm^{-3}}
\end{aligned}
$$
$$n_0=\frac{n_i^2}{p_0}=\frac{(1.8\times10^{6}\unit{cm^{-3}})^2}{3.000\times10^{15}\unit{cm^{-3}}}=1.08\times10^{-3}\unit{cm^{-3}}$$

### (c)
It means that there is about only one minor minority carrier every $10^3\unit{cm^3}$.

## Ex 3.2

### (a)
$$N_a=3\times10^{16}\unit{cm^{-3}},N_d=1.5\times10^{16}\unit{cm^{-3}}$$
$$n_i=1.5\times10^{10}\unit{cm^{-3}}$$
Since $N_a>N_d$, it is p-type. And $n_i\ll N_a-N_d$, so the majority carriers are holes, the concentration is
$$p_0=N_a-N_d=3\times10^{16}\unit{cm^{-3}}-1.5\times10^{16}\unit{cm^{-3}}=1.5\times10^{16}\unit{cm^{-3}}$$
The minority carriers are electrons, the concentration is
$$n_0=\frac{n_i^2}{p_0}=\frac{(1.5\times10^{10}\unit{cm^{-3}})^2}{1.5\times10^{16}\unit{cm^{-3}}}=1.5\times10^{4}\unit{cm^{-3}}$$

### (b)
$$p_0=N_a+\Delta N_a-N_d$$
$$\Delta N_a'=p_0-(N_a-N_d)=5\times10^{16}\unit{cm^{-3}}-1.5\times10^{16}\unit{cm^{-3}}=3.5\times10^{16}\unit{cm^{-3}}$$
$$n_0=\frac{n_i^2}{p_0}=\frac{(1.5\times10^{10}\unit{cm^{-3}})^2}{5\times10^{16}\unit{cm^{-3}}}=4.5\times10^{3}\unit{cm^{-3}}$$

## Ex 3.3

### (a)
$$n_0=\frac{N_d}{2}+\sqrt{\left(\frac{N_d}{2}\right)^2+n_i^2}=\frac{N_d}{0.95}=1.05\times10^{15}\unit{cm^{-3}}$$
$$n_i^2=\left(\frac{N_d}{0.95}-\frac{N_d}{2}\right)^2-\left(\frac{N_d}{2}\right)^2=\left(\frac{10^{15}\unit{cm^{-3}}}{0.95}-\frac{10^{15}\unit{cm^{-3}}}{2}\right)^2-\left(\frac{10^{15}\unit{cm^{-3}}}{2}\right)^2=5.25\times10^{28}\unit{cm^{-6}}$$
$$n_i^2=N_cN_v\left(\frac{T}{T_0}\right)^3\exp\left[\frac{-E_g}{kT}\right]$$
$$5.25\times10^{28}\unit{cm^{-6}}=2.8\times10^{19}\unit{cm^{-3}}\cdot1.04\times10^{19}\unit{cm^{-3}}\left(\frac{T}{300\unit{K}}\right)^3\exp\left[\frac{-1.12\unit{eV}}{8.62\times10^{-5}\unit{eV/K}\cdot T}\right]$$
$$T=537.25\unit{K}$$

### (b)
For $T=300K$,
$$E_c-E_F=kT\ln\left[\frac{N_c}{n_0}\right]=0.0259\unit{eV}\ln\left[\frac{2.8\times10^{19}\unit{cm^{-3}}}{1.05\times10^{15}\unit{cm^{-3}}}\right]=2.64\times10^{-1}\unit{eV}$$
For $T=537.25\unit{K}$,
$$kT=8.62\times10^{-5}\unit{eV/K}\cdot537.25\unit{K}=4.63\times10^{-2}\unit{eV}$$
$$N_c'=N_c\left(\frac{T}{T_0}\right)^{3/2}=2.8\times10^{19}\unit{cm^{-3}}\cdot\left(\frac{537.25\unit{K}}{300\unit{K}}\right)^{3/2}=6.71\times10^{19}\unit{cm^{-3}}$$
$$E_c-E_F=kT\ln\left[\frac{N_c}{n_0}\right]=4.63\times10^{-2}\unit{eV}\ln\left[\frac{6.71\times10^{19}\unit{cm^{-3}}}{1.05\times10^{15}\unit{cm^{-3}}}\right]=5.12\times10^{-1}\unit{eV}$$
So
$$\Delta(E_c-E_F)=5.12\times10^{-1}\unit{eV}-2.64\times10^{-1}\unit{eV}=2.48\times10^{-1}\unit{eV}$$

### (c)
It is closer to the intrinsic value at high temperature.

## Ex 3.4

### (a)
$$E_{Fi}-E_{midgap}=\frac{3}{4}kT\ln\left[\frac{m_p^*}{m_n^*}\right]=\frac{3}{4}\cdot0.0259\unit{eV}\cdot\ln10=4.47\times10^{-2}\unit{eV}$$

### (b)

#### (i)
Since impurity atoms are added so that $E_{Fi}<E_{midgap}$, it is p-type, acceptors should be added.

#### (ii)
$$E_{Fi}-E_F=0.45\unit{eV}+4.47\times10^{-2}\unit{eV}=0.494\unit{eV}$$
$$p_0=n_i\exp\left[\frac{E_{Fi}-E_F}{kT}\right]=10^5\unit{cm^{-3}}\cdot\exp\left[\frac{0.494\unit{eV}}{0.0259\unit{eV}}\right]=1.92\times10^{13}\unit{cm^{-3}}$$

## Ex 3.5

### (a)
When replacing gallium, silcon is the donor,
$$N_d=0.05\cdot7\times10^{15}\unit{cm^{-3}}=3.5\times10^{14}\unit{cm^{-3}}$$
When replacing arsenic, silcon is the accepetor,
$$N_a=0.95\cdot7\times10^{15}\unit{cm^{-3}}=6.65\times10^{15}\unit{cm^{-3}}$$

### (b)
Since $N_a>N_d$, it is p-type.

### (c)
$$n_i=1.8\times10^{6}\unit{cm^{-3}}$$
Since $n_i\ll N_a-N_d$, so the majority carriers are holes, the concentration is
$$p_0=N_a-N_d=6.65\times10^{15}\unit{cm^{-3}}-3.5\times10^{14}\unit{cm^{-3}}=6.3\times10^{15}\unit{cm^{-3}}$$
The minority carriers are electrons, the concentration is
$$n_0=\frac{n_i^2}{p_0}=\frac{(1.8\times10^{6}\unit{cm^{-3}})^2}{6.3\times10^{15}\unit{cm^{-3}}}=5.14\times10^{-4}\unit{cm^{-3}}$$

### (d)
$$E_{Fi}-E_F=kT\ln\left[\frac{p_0}{n_i}\right]=0.0259\unit{eV}\ln\left[\frac{6.3\times10^{15}\unit{cm^{-3}}}{1.8\times10^{6}\unit{cm^{-3}}}\right]=5.69\times10^{-1}\unit{eV}$$

## Ex 3.6

### (a)
$$R=\frac{V}{I}=\frac{10\unit{V}}{100\unit{mA}}=100\unit{\Omega}$$

### (b)
$$\sigma=\frac{L}{RA}=\frac{10^{-3}\unit{cm}}{100{\Omega}\cdot0.001\unit{cm^2}}=0.01(\Omega\cdot cm)^{-1}$$

### (c)
$$\sigma\approx e\mu_nN_d$$
$$N_d\approx\frac{\sigma}{e\mu_n}=\frac{0.01(\Omega\cdot cm)^{-1}}{1.6\times10^{-19}\unit{C}\cdot1350\unit{cm^2/V\cdot s}}=4.63\times10^{13}\unit{cm^{-3}}$$

### (d)
$$\sigma\approx e\mu_p(N_a-N_d)$$
$$N_a\approx\frac{\sigma}{e\mu_p}+N_d=\frac{0.01(\Omega\cdot cm)^{-1}}{1.6\times10^{-19}\unit{C}\cdot480\unit{cm^2/V\cdot s}}+10^{15}\unit{cm^{-3}}=1.13\times10^{15}\unit{cm^{-3}}$$

## Ex 3.7

### (a)
According to Figure 5.3, when $N_a=2\times10^{16}\unit{cm^{-3}}$, $\mu_p=400\unit{cm^2/V\cdot s}$.
$$R=\frac{L}{\sigma A}\approx\frac{L}{e\mu_pN_aA}=\frac{0.075cm}{1.6\times10^{-19}\unit{C}\cdot400\unit{cm^2/V\cdot s}\cdot2\times10^{16}\unit{cm^{-3}}\cdot8.5\times10^{-4}\unit{cm^2}}=68.93\unit{\Omega}$$
$$I=\frac{V}{R}=\frac{2\unit{V}}{68.93\unit{\Omega}}=2.90\times10^{-2}\unit{A}$$

### (b)
$$R'=3R=3\times68.93\unit{\Omega}=206.79\unit{\Omega}$$
$$I=\frac{V}{R}=\frac{2\unit{V}}{206.79\unit{\Omega}}=9.67\times10^{-3}\unit{A}$$

### (c)
$$J=ep_0v_d$$
$$v_d=\frac{J}{ep_0}=\frac{I}{ep_0A}$$
For (a),
$$v_d=\frac{I}{ep_0A}=\frac{2.90\times10^{-2}\unit{A}}{1.6\times10^{-19}\unit{C}\cdot2\times10^{16}\unit{cm^{-3}}\cdot8.5\times10^{-4}\unit{cm^2}}=1.07\times10^4\unit{cm/s}$$
For (b),
$$v_d=\frac{I}{ep_0A}=\frac{9.67\times10^{-3}\unit{A}}{1.6\times10^{-19}\unit{C}\cdot2\times10^{16}\unit{cm^{-3}}\cdot8.5\times10^{-4}\unit{cm^2}}=3.55\times10^3\unit{cm/s}$$

## Ex 3.8

$$\sigma=e\mu_nN_d$$

### (a)
```{r ex8.a, fig.height=4, fig.width=7}
func <- function(x) {1.6e-19*1350/(1+x/5e16)*x}
curve(func, from = 1e15, to = 1e18, xlab = TeX('$N_d(cm^{-3})$'), 
      ylab = TeX('$\\sigma((\\Omega\\cdot cm)^{-1})$'), log = 'x')
```

### (b)
```{r ex8.b, fig.height=4, fig.width=7}
func <- function(x) {1.6e-19*1350*x}
curve(func, from = 1e15, to = 1e18, xlab = TeX('$N_d(cm^{-3})$'), 
      ylab = TeX('$\\sigma((\\Omega\\cdot cm)^{-1})$'), log = 'x')
```

$$J=\sigma E$$

### (c)
```{r ex8.c, fig.height=4, fig.width=7}
func <- function(x) {1.6e-19*1350/(1+x/5e16)*x*10}
curve(func, from = 1e15, to = 1e18, xlab = TeX('$N_d(cm^{-3})$'), 
      ylab = TeX('$J(A/cm^2)$'), log = 'x')
```

### (d)
```{r ex8.d, fig.height=4, fig.width=7}
func <- function(x) {1.6e-19*1350*x*10}
curve(func, from = 1e15, to = 1e18, xlab = TeX('$N_d(cm^{-3})$'), 
      ylab = TeX('$J(A/cm^2)$'), log = 'x')
```

## Ex 3.9

### (a)
$$J=e\mu_nn(x)E+eD_n\frac{dn(x)}{dx}$$
$$\frac{dn(x)}{dx}+\frac{\mu_n E}{D_n}n(x)=\frac{J}{eD_n}$$
$$p=p(x)=\frac{\mu_n E}{D_n},q=q(x)=\frac{J}{eD_n}$$
$$n(x)=n_0e^{-\int_{x_0}^xp(x)dx}+\int_{x_0}^xq(s)e^{-\int_s^xp(t)dt}ds$$
When $x_0=0$, $e\mu_nn_0E=J/2$, $n_0=\frac{J}{2e\mu_nE}$,
$$n(x)=\frac{J}{2e\mu_nE}e^{-px}+\int_0^xqe^{-p(x-s)}ds=\left(\frac{J}{2e\mu_nE}-\frac{q}{p}\right)e^{-px}+\frac{q}{p}=-\frac{J}{2e\mu_nE}\exp\left[-\frac{\mu_n E}{D_n}x\right]+\frac{J}{e\mu_nE}$$
$$\frac{J}{e\mu_nE}=\frac{100}{1.6\times10^{-19}\cdot8000\cdot12}=6.51\times10^{15}$$
$$\frac{\mu_nE}{D_n}=\frac{\mu_nE}{kT\mu_n}=\frac{E}{kT}=\frac{12}{0.0259}=463.32$$
$$n(x)=-3.255\times10^{15}e^{-463.32x}+6.51\times10^{15}\unit{cm^{-3}}$$

### (b)
$$n(0)=3.255\times10^{15}\unit{cm^{-3}}$$
$$n(50\times10^{-4})=6.189\times10^{15}\unit{cm^{-3}}$$

### (c)
$$J_{drf}=e\mu_nn(50\times10^{-4})E=1.6\times10^{-19}\cdot8000\unit{cm^2/V\cdot s}\cdot6.189\times10^{15}\unit{cm^{-3}}\cdot12\unit{V/cm}=95.06\unit{A/cm^2}$$
$$J_{diff}=J-J_{drf}=100\unit{A/cm^2}-95.06\unit{A/cm^2}=4.94\unit{A/cm^2}$$

## Ex 3.10

### (a)
$$E(x)=-\frac{kT}{e}\cdot\frac{1}{N_d}\cdot\frac{dN_d(x)}{dx}=\frac{kT}{e}\cdot\frac{\frac{1}{L}N_{d_0}e^{-x/L}}{N_{d_0}e^{-x/L}}=\frac{kT}{eL}=\frac{0.0259\unit{V}}{10\times10^{-4}\unit{cm}}=25.9\unit{V/cm}$$

### (b)
$$\Delta V=\int_L^0E(x)dx=-25.9\unit{V/cm}\cdot10\times10^{-4}\unit{cm}=-0.0259\unit{V}$$





